Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
All capacity factors are much closer to 80%
Update notation for consistency

In each of the four cases, the initial 100 LWRs are modified to have a zero
length refueling outage with an explicit 900 MWe net power output capacity.  Because the
individual reactor model doesn't have any way to start a reactor mid-cycle,
this was done to avoid having all initial LWRs refuel at the same time.  The
parameters for each case were also selected to keep capacity factors for
individual reactors very roughly around 90\%.

@@

One difference between the fleet and individual facility modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short one half batch of fuel, it will produce $\frac{2.5}{3}\cdot C$
of power for that time step where $C$ is the power capacity of a single
reactor of the fleet (e.g. 1000 MWe).  If an individually modeled reactor is
short a half batch of fuel, then it will produce no power ($0 \cdot C$) that
time step.  Time step duration can also have this effect.  For both fleet and
individual reactor modeling, power goes offline in full time step increments.
For example, if a 3-batch fleet based reactor is short $\frac{1}{2}$ batch of
fuel with a 3 month time step, then it will produce $\frac{2.5}{3} \cdot 3
\text{mo} \cdot C $ of energy.  In contrast, a monthly time step might allow
the same reactor to produce $[\frac{5}{6} \cdot 1 \text{mo} + 1 \cdot 2
\text{mo}] \cdot C $ of energy if the fuel shortage actually ended after only
1 month.  Quantifying this effect directly is difficult.  One way of observing
it is to compare fleet reactor scenarios that have different time step
durations (i.e. cases MF and QF).  Because the fleet reactors have perfect fuel
sharing (described below) and no noise from refueling outages, differences observed will
likely be due to quantized shutdown.

>>>>

In each of the four cases, the initial 100 LWRs are modified to have a zero
length refueling outage with an explicit 900 MWe net power output capacity.  Because the
individual reactor model doesn't have any way to start a reactor mid-cycle,
this was done to avoid having all initial LWRs refuel at the same time.  The
parameters for each case were also selected to keep capacity factors for
individual reactors very roughly around 80\%.

@@

One difference between the fleet and individual facility modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short one half batch of fuel, it will produce $\frac{2.5}{3}\cdot P_r$
of power for that time step where $P_r$ is the power capacity of a single
reactor of the fleet (e.g. 1000 MWe).  If an individually modeled reactor is
short a half batch of fuel, then it will produce no power ($0 \cdot P_r$) that
time step.  Time step duration can also have this effect.  For both fleet and
individual reactor modeling, power goes offline in full time step increments.
For example, if a 3-batch fleet based reactor is short $\frac{1}{2}$ batch of
fuel with a 3 month time step, then it will produce $\frac{2.5}{3} \cdot 3
\text{mo} \cdot P_r$ of energy.  In contrast, a monthly time step might allow
the same reactor to produce $[\frac{5}{6} \cdot 1 \text{mo} + 1 \cdot 2
\text{mo}] \cdot P_r $ of energy if the fuel shortage actually ended after only
1 month.  Quantifying this effect directly is difficult.  One way of observing
it is to compare fleet reactor scenarios that have different time step
durations (i.e. cases MF and QF).  Because the fleet reactors have perfect fuel
sharing (described below) and no noise from refueling outages, differences observed will
likely be due to quantized shutdown.
